Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
discussion example disk

\begin{example}
\vincent{Example with the disk}
\end{example}

@@

\begin{proof}
\vincent{Careful: arcs / curves.}
Let~$\alpha$ be a~$\dissection$-accordion.
Let~$a$,~$b$,~$c$ be three consecutive edges of~$\dissection$ crossed by~$\alpha$.
Let~$u \in \dissection$ be the common endpoint of~$a$ and $b$ given by Definition~\ref{def:accordion} and let~$v \in \dissection$ be the common endpoint of~$b$ and~$c$.
If $u = v$, then the segment of~$\alpha$ between~$a$ and~$c$ stays in the same face of~$\dissection\dual$.
Otherwise, when crossing~$b$, the accordion~$\alpha$ leaves the face~$u\dual$ of $\dissection\dual$ and enters the face~$v\dual$.
In the surface obtained by glueing the two cells~$u\dual$ and~$v\dual$ along~$b\dual$, the marked points~$u$ and~$v$ are separated by~$\alpha$.
Conversely, assume that~$\alpha$ is an arc of~$(\surface, B)$ which is not a $\dissection$-accordion.
We are in one of the following cases.

Case 1: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
Consider the connected component of~$f\setminus\alpha$ that do not contain~$f\dual$.
The boundary of this component contains an arc~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
Let~$u,v$ be the endpoints of~$c$.
Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected component, one containing both endpoints of~$\delta$.

Case 2: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that do not contain~$u$.

Case 3: The arc~$\alpha$ consecutively crosses two arcs~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
This contradicts the assumption that the dissections~$\dissection$ and~$\dissection\dual$ are dual to each other.

Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
There is a~$\dissection\dual$-arc~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
\end{proof}

@@

>>>>

@@

\begin{proof}
Let~$\alpha$ be a~$\dissection$-accordion.
Let~$a$,~$b$,~$c$ be three consecutive edges of~$\dissection$ crossed by~$\alpha$.
Let~$u \in \dissection$ be the common endpoint of~$a$ and $b$ given by Definition~\ref{def:accordion} and let~$v \in \dissection$ be the common endpoint of~$b$ and~$c$.
If $u = v$, then the segment of~$\alpha$ between~$a$ and~$c$ stays in the same face of~$\dissection\dual$.
Otherwise, when crossing~$b$, the accordion~$\alpha$ leaves the face~$u\dual$ of $\dissection\dual$ and enters the face~$v\dual$.
In the surface obtained by glueing the two cells~$u\dual$ and~$v\dual$ along~$b\dual$, the marked points~$u$ and~$v$ are separated by~$\alpha$.
Conversely, assume that~$\alpha$ is an curve of~$(\surface, B)$ which is not a $\dissection$-accordion.
We are in one of the following cases.

Case 1: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
Consider the connected component of~$f\setminus\alpha$ that do not contain~$f\dual$.
The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
Let~$u,v$ be the endpoints of~$c$.
Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected component, one containing both endpoints of~$\delta$.

Case 2: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share a unique common endpoint, but the region delimited by~$\alpha$,~$a$ and~$b$ is not a disk.
Since the dissection~$\dissection$ is cellular, that region has to contain some marked point~$u \in \dissection\dual$.
One conclude that~$\alpha$ is not a~$\dissection\dual$-slalom similarly as in the first case, by considering the component of~$u\dual \setminus \alpha$ that do not contain~$u$.

Case 3: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that share two different endpoints, and none of the two regions delimited by~$\alpha$,~$a$ and~$b$ is a disk.
Since the dissection~$\dissection$ is cellular, both regions have to contain a puncture.
This contradicts the assumption that the dissections~$\dissection$ and~$\dissection\dual$ are dual to each other.

Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
There is a~$\dissection\dual$-edge~$a$ ending in that puncture. When~$\alpha$ crosses~$a$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
\end{proof}

@@

\begin{example}
When the dissection~$\dissection$ is a classical dissection of a polygon (with no puncture) where each cell has at most one boundary edge, the dual dissection~$\dissection\dual$ is a tree.
The non-kissing complex in his situation was treated in detail in~\cite{GarverMcConville, MannevillePilaud-accordion}.
Note that even when the surface~$\surface$ is a disk, we authorize here both~$\dissection$ and~$\dissection\dual$ to have interior faces and punctures.
\end{example}
